openTSNE: a modular \proglang{Python} library for t-SNE dimensionality reduction and embedding

### 2022-04-08 paper/main.tex
Better integrate the code snippets into the text

%% - \Abstract{} almost as usual
\Abstract{
One of the most popular techniques for constructing visualizations of large, high-dimensional data sets is $t$-distributed stochastic neighbor embedding (t-SNE). Recently, several extensions have been proposed to address scalability issues and the quality of the resulting visualizations. We introduce \opentsne, a modular Python library that implements the core t-SNE algorithm and its many extensions. The library is fast and can treat data sets containing millions of data points. \opentsne\ is open-source and is distributed under the BSD-3-Clause License. Its source code is available at \url{https://github.com/pavlin-policar/openTSNE}.
}

@@

However, easy access to efficient implementations almost universally correlates with the widespread adoption of novel computational techniques. Despite the many theoretical advancements, most popular t-SNE libraries have been slow to incorporate them into their implementations. In this paper, we present \opentsne, our open-source Python implementation of t-SNE, complete with its recently proposed extensions. \opentsne\ is easy to install and includes precompiled binaries available through popular Python package managers. It provides a familiar API, making it suitable as a drop-in replacement for existing t-SNE implementations.

@@

We introduce \opentsne, a comprehensive Python library that implements the t-SNE algorithm and its numerous recently proposed extensions. \opentsne\ is designed to accommodate all types of users and includes both a simple API that allows users to quickly obtain informative t-SNE visualizations, as well as a more flexible API that allows seasoned practitioners to modify all the
different aspects of the t-SNE algorithm.

@@

\section{Discussion and Examples} \label{sec:discussion}

@@

Dimensionality reduction techniques implicitly assume that high-dimensional data
lies on a lower-dimensional manifold, which a small number of dimensions can
accurately capture. However, there is no evidence that every data set can
accurately be described using only two dimensions, and any such embedding will
inevitably lead to a loss of information. Thus, it is beneficial to examine
multiple embeddings, each of which provides a different perspective on topology
and other data characteristics.

@@

We illustrate this point by generating four different embeddings of the data on
single-cell gene expression in mouse brain~\citep{tasic2018shared}.
Fig.~\ref{fig:tasic}.a shows an embedding using default t-SNE parameters. We generate
the four different embeddings using the following code snippet (shortened for clarity).
\begin{CodeChunk}
\begin{CodeInput}
embedding_a = openTSNE.TSNE(perplexity=30).fit(x)
embedding_b = openTSNE.TSNE(perplexity=500).fit(x)
embedding_c = openTSNE.TSNE(perplexity=[30, 500]).fit(x)
embedding_d = openTSNE.TSNE(perplexity=30, dof=0.6).fit(x)
\end{CodeInput}
\end{CodeChunk}
While different clusters of excitatory and inhibitory neurons appear close to one another, all clusters appear equidistant from their neighbors, and the overall relations between groups are not obvious. The embedding in Fig.~\ref{fig:tasic}.b focuses on preserving larger neighborhoods of points, resulting in a more globally consistent layout where relations between clusters become more apparent. Here, it is evident from the increased white space between groups that there is one large class of excitatory neurons and two related classes of inhibitory neurons. Unfortunately, focusing on preserving large neighborhoods leads to the absorption of smaller clusters into larger ones. Alternatively, Fig.~\ref{fig:tasic}.c uses multi-scale similarity kernels that aim to preserve both the global organization of clusters and prevent smaller cluster absorption. We constructed the embedding from Fig.~\ref{fig:tasic}.d with the settings used for Fig.~\ref{fig:tasic}.a, but at a finer level of resolution. The figure demonstrates that some clusters are composed of numerous, smaller subgroups representing different cell subpopulations that are not visible under standard parameter settings.

@@

When dealing with data containing millions of data points, standard t-SNE
embeddings often become unwieldy -- cluster boundaries are blurred, large
clusters absorb smaller ones, and relationships between clusters become
increasingly difficult to interpret. We constructed Fig.~\ref{fig:cao}.a from
the data containing expression profiles of over two million single cells
captured at different time points in mouse development. The embedding indicates
numerous clusters with transitions between time points, as marked by the
color-coding, that are difficult to interpret. \citet{kobak2019art} that
increasing attractive forces between similar data points controlled via
the \textit{exaggeration} parameter leads to more compact clusters, and
subsequently, more informative visualizations. For instance, \ref{fig:cao}.b
doubles the default exaggeration, which uncovers some
of the data's overall structure. Further doubling the exaggeration in
\ref{fig:cao}.c allows us to observe that the data is comprised of two main groups
of cells and eight somewhat smaller clusters. The visualization also reveals
several tiny clusters, possibly corresponding to rare cell types.
\begin{CodeChunk}
\begin{CodeInput}
# To improve the global structure of the final layout, we initialize the
# embedding by creating a t-SNE plot on a sample of points

@@

# Lastly, we merge `init_sample` and `init_rest` and restore the original order
init_full = np.vstack((init_sample, init_rest))[reverse]
\end{CodeInput}
\end{CodeChunk}
We generate the three different embeddings using the following code snippet
(shortened for clarity).
\begin{CodeChunk}
\begin{CodeInput}
# We separately precompute the affinities as this can take quite a long time.
# This way, we can reuse the precomputed affinities in various different
# embeddings, without having to repeat the same, costly computation every time.
affinities = openTSNE.affinity.PerplexityBasedNN(x, perplexity=30)

@@

Figs.~\ref{fig:macosko}.b and \ref{fig:macosko}.c demonstrate how we can use a
previously labeled single-cell data set and embed cells from a separate
experiment into the reference landscape. The reference data from
\citet{macosko2015highly} contains gene expression profiles from mouse retinal
cells. By embedding the samples from a similar experiment on bipolar retinal
cells by \citet{shekhar2016comprehensive}, we can correctly map the bipolar
cell clusters onto the reference embedding. The following snippet shows the
code necessary to generate figure~\ref{fig:macosko}.
\begin{CodeChunk}
\begin{CodeInput}
# We specify the old default parameter values which are often used to show
# why t-SNE misbehaves or fails to preserve global structure
tsne_old = openTSNE.TSNE(
    initialization="random", learning_rate=200, n_iter=750
).fit(x)

@@

Embedding single cells into existing reference atlases can also be useful for
cell-type classification in cases of unknown cell identities. For instance, in
Fig.~\ref{fig:transform}, we construct a reference embedding using labeled data
from \citet{hochgerner2018conserved} containing gene-expression profiles of
cells from the mouse brain. The authors assign a type to each cell. We can
verify their classification accuracy by visualizing the expression of
well-established gene markers for the major cell types. We then embed cells
from \citet{harris2018classes} into the constructed cell atlas. In
\citet{harris2018classes}, labels are provided only for neuronal cells. In the
resulting mapping, we can quickly identify other non-neuronal cell types,
including oligodendrocytes and astrocytes. We can further use marker genes to
validate that the mapping in the reference landscape is correct.

@@

@@

% We benchmark Python
Fig.~\ref{fig:benchmarks_py} benchmarks four popular Python~\citep{vanrossum1995python} t-SNE
implementations, including \pkg{scikit-learn} (v1.0.1), \pkg{MulticoreTSNE}
(v0.1), \pkg{FIt-SNE} (v1.1.0), and \opentsne\ (v0.6.2). Benchmarks were
performed on an Intel(R) Xeon(R) CPU E5-1650 equipped with 128 GB of memory.
Benchmarks were run for $1,000$ iterations with the original t-SNE parameters,
as some implementations do not allow for their modification. To ensure a
realistic benchmarking scenario, we utilize the 10X Genomics 1.3 million mouse
brain data set~\citep{xxx}, containing 1.3 million single-cell gene-expression
profiles. We preprocess the data using the standard single-cell analysis
pipeline~\citep{xxx} and extract the top 50 principal components. To generate
benchmark data sets of different sample sizes, we subsample the data set five
times at each sample size. In total, we run each implementation on 30 different
data sets.

@@

% Problem with Python
In Python, the most widely-used implementation of t-SNE comes from \pkg{scikit-learn}, which exhibits long runtimes when compared to other Python implementations. \pkg{scikit-learn}, like its \proglang{C++} counterpart -- \pkg{MulticoreTSNE}~\citep{Ulyanov2016} , is based on the Barnes-Hut approximation scheme. However, as shown on Fig.~\ref{fig:benchmarks_py}, \pkg{scikit-learn} exhibits much longer runtimes than \pkg{MulticoreTSNE}. Newer implementations, such as \pkg{FIt-SNE} and \opentsne, both implement the FIt-SNE approximation scheme, making them suitable for the visualization of millions of data points. While both libraries implement the same algorithm, \opentsne\ emphasizes ease of use and extensibility and is primarily written in Python, which inevitably introduces some runtime overhead. This makes \opentsne\ marginally slower than its pure \proglang{C++} counterpart -- \pkg{FIt-SNE}. However, these differences disappear almost entirely when utilizing multi-threading, as shown in Fig.~\ref{fig:benchmarks_py}. Additionally, \opentsne\ provides a flexible API, allowing the user to split up the embedding-construction process into several parts. This allows us to cache and reuse intermediate results, enabling users to quickly experiment with different parameter settings and iterate on their final visualizations. This kind of functionality is not supported in other implementations, which require the user to start from scratch for every embedding, resulting in large amounts of redundant computation.

@@

\begin{figure*}[ht]
  \centering
  \includegraphics[width=0.75\textwidth]{benchmarks_langs-final}
  %\includegraphics[width=\textwidth]{benchmarks-combined}
  \caption{\label{fig:benchmarks_lang}
  We select the fastest available, open-source implementations of the t-SNE
  algorithm from the \proglang{Python}, \proglang{R}, and \proglang{Julia}
  programming languages. We choose
  \opentsne\ (v0.6.2) for Python, \pkg{Rtsne}~\citep{krijthe2015rtsne} (v0.15)
  for \proglang{R}, and \pkg{TSne.jl}~\citep{julia_tsne} (v1.3.0) for
  \proglang{Julia}. The benchmarks reflect the time complexity of the
  implemented approximation schemes. For instance, \pkg{TSne.jl} implements a
  naive $\mathcal{O}(N^2)$ algorithm, making it prohibitively expensive for all
  but the smallest of data sets. \pkg{Rtsne} scales similarily to
  \pkg{MulticoreTSNE} in Python, as it implements the $\mathcal{O}(N \log N)$
  Barnes-Hut approximation scheme. Interestingly, the multi-threaded
  implementation version of \pkg{Rtsne} crashes on benchmark data sets
  containing over 500,000 data points due to lack of stack memory. We found
  these crashes to be inconsistent and somewhat random. \opentsne\ is the only
  library implementing the more recent FIt-SNE approximation scheme, which makes
  it suitable for larger data sets.
}
\end{figure*}

@@

We designed \opentsne\ to be accessible to a broader audience. We provide
precompiled binaries for all major Python versions on all major platforms,
making the installation process as seamless as possible. One can install
\opentsne\ through the Python Package Index (\pkg{PyPI}) or \pkg{conda} from the
\pkg{conda-forge} channel, the two most widely adopted Python package managers.
\opentsne's high-level interface is inspired by \pkg{scikit-learn}, which is well
established in the Python data science ecosystem. \opentsne\ implements
multi-threaded versions of both the Barnes-Hut and FIt-SNE approximation
schemes, enabling it to be applied to data sets containing millions of data
points. While the Python virtual machine inevitably introduces some performance
overhead, the runtime is comparable to its \proglang{C++} counterpart -- \pkg{FIt-SNE}.
Finally, \opentsne\ is extensible. Its modular design enables researchers to
quickly experiment with different parameter settings and easily incorporate
custom components into the software. We provide an extended list of features and
comparison to other popular t-SNE implementations in Tab.~\ref{tab:features}.

@@

\toprule
\textbf{Ease of Installation} \\
Native Python installation & \checkmark & & & \checkmark & & \\
\pkg{PyPI} package & \checkmark & \checkmark & & \checkmark & & \\
\pkg{conda} package & \checkmark & & & \checkmark & & \\

@@

We introduce \opentsne, the most feature-complete, open-source, Python
implementation of the widely popular t-SNE visualization algorithm. The library
incorporates the latest developments to the t-SNE algorithm and makes them
easily accessible through a familiar API. \opentsne\ implements efficient
approximation schemes, making it suitable for the visualization of large data
sets containing up to millions of data points. Finally, \opentsne\ is easy to
install and comes with precompiled binaries available for all major platforms.

>>>>

%% - \Abstract{} almost as usual
\Abstract{
One of the most popular techniques for constructing visualizations of large, high-dimensional data sets is $t$-distributed stochastic neighbor embedding (t-SNE). Recently, several extensions have been proposed to address scalability issues and the quality of the resulting visualizations. We introduce \opentsne, a modular \proglang{Python} library that implements the core t-SNE algorithm and its many extensions. The library is fast and can treat data sets containing millions of data points. \opentsne\ is open-source and is distributed under the BSD-3-Clause License. Its source code is available at \url{https://github.com/pavlin-policar/openTSNE}.
}

@@

However, easy access to efficient implementations almost universally correlates with the widespread adoption of novel computational techniques. Despite the many theoretical advancements, most popular t-SNE libraries have been slow to incorporate them into their implementations. In this paper, we present \opentsne, our open-source \proglang{Python} implementation of t-SNE, complete with its recently proposed extensions. \opentsne\ is easy to install and includes precompiled binaries available through popular \proglang{Python} package managers. It provides a familiar API, making it suitable as a drop-in replacement for existing t-SNE implementations.

@@

We introduce \opentsne, a comprehensive \proglang{Python} library that implements the t-SNE algorithm and its numerous recently proposed extensions. \opentsne\ is designed to accommodate all types of users and includes both a simple API that allows users to quickly obtain informative t-SNE visualizations, as well as a more flexible API that allows seasoned practitioners to modify all the
different aspects of the t-SNE algorithm.

@@

\section{Case Studies} \label{sec:discussion}

@@

Dimensionality reduction techniques implicitly assume that high-dimensional data
lies on a lower-dimensional manifold, which can accurately be captured by a small number of dimensions. However, there is no evidence that every data set can
accurately be described using only two dimensions, and any such embedding will
inevitably lead to a loss of information. Thus, it is beneficial to examine
multiple embeddings, each of which provides a different perspective on topology
and other data characteristics.

@@

We illustrate this point by generating four different embeddings of the data on
single-cell gene expression in mouse brain~\citep{tasic2018shared}. We generate
the embeddings using the following code snippet (shortened for clarity):
\begin{CodeChunk}
\begin{CodeInput}
embedding_a = openTSNE.TSNE(perplexity=30).fit(x)
embedding_b = openTSNE.TSNE(perplexity=500).fit(x)
embedding_c = openTSNE.TSNE(perplexity=[30, 500]).fit(x)
embedding_d = openTSNE.TSNE(perplexity=30, dof=0.6).fit(x)
\end{CodeInput}
\end{CodeChunk}
Fig.~\ref{fig:tasic}.a shows an embedding using default t-SNE parameters.
While different clusters of excitatory and inhibitory neurons appear close to one another, all clusters appear equidistant from their neighbors, and the overall relations between groups are not obvious. The embedding in Fig.~\ref{fig:tasic}.b focuses on preserving larger neighborhoods of points, resulting in a more globally consistent layout where relations between clusters become more apparent. Here, it is evident from the increased white space between groups that there is one large class of excitatory neurons and two related classes of inhibitory neurons. Unfortunately, focusing on preserving large neighborhoods leads to the absorption of smaller clusters into larger ones. Alternatively, Fig.~\ref{fig:tasic}.c uses multi-scale similarity kernels that aim to preserve both the global organization of clusters and prevent smaller cluster absorption. We constructed the embedding from Fig.~\ref{fig:tasic}.d with the settings used for Fig.~\ref{fig:tasic}.a, but at a finer level of resolution. The figure demonstrates that some clusters are composed of numerous, smaller subgroups representing different cell subpopulations that are not visible under standard parameter settings.

@@

When dealing with data containing millions of data points, standard t-SNE
embeddings often become unwieldy -- cluster boundaries are blurred, large
clusters absorb smaller ones, and relationships between clusters become
increasingly difficult to interpret. We constructed Fig.~\ref{fig:cao}.a from
the data containing expression profiles of over two million single cells
captured at different time points in mouse development. The embedding indicates
numerous clusters with transitions between time points, as marked by the
color-coding, that are difficult to interpret. \citet{kobak2019art} that
increasing attractive forces between similar data points controlled via
the \textit{exaggeration} parameter leads to more compact clusters, and
subsequently, more informative visualizations. For instance, \ref{fig:cao}.b
doubles the default exaggeration, which uncovers some
of the data's overall structure. Further doubling the exaggeration in
\ref{fig:cao}.c allows us to observe that the data is comprised of two main groups
of cells and eight somewhat smaller clusters. The visualization also reveals
several tiny clusters, possibly corresponding to rare cell types.

Figs.~\ref{fig:cao}.a-c were generated using the following code snippet, which demonstrates how we can take advantage of the more advanced features of \opentsne\ to more quickly create meaningful visualizations of massive data sets. We first take a sample of the data and use t-SNE to construct a globally consistent initialization, which will then be used to initialize the remaning data points:
\begin{CodeChunk}
\begin{CodeInput}
# To improve the global structure of the final layout, we initialize the
# embedding by creating a t-SNE plot on a sample of points

@@

# Lastly, we merge `init_sample` and `init_rest` and restore the original order
init_full = np.vstack((init_sample, init_rest))[reverse]
\end{CodeInput}
\end{CodeChunk}
We then generate the three different embeddings using the following code snippet
(shortened for clarity):
\begin{CodeChunk}
\begin{CodeInput}
# We separately precompute the affinities as this can take quite a long time.
# This way, we can reuse the precomputed affinities in various different
# embeddings, without having to repeat the same, costly computation every time.
affinities = openTSNE.affinity.PerplexityBasedNN(x, perplexity=30)

@@

Figs.~\ref{fig:macosko}.b and \ref{fig:macosko}.c demonstrate how we can use a
previously labeled single-cell data set and embed cells from a separate
experiment into the reference landscape. The reference data from
\citet{macosko2015highly} contains gene expression profiles from mouse retinal
cells. By embedding the samples from a similar experiment on bipolar retinal
cells by \citet{shekhar2016comprehensive}, we can correctly map the bipolar
cell clusters onto the reference embedding. The following snippet shows the
code necessary to generate Fig.~\ref{fig:macosko}:
\begin{CodeChunk}
\begin{CodeInput}
# We specify the old default parameter values which are often used to show
# why t-SNE misbehaves or fails to preserve global structure
tsne_old = openTSNE.TSNE(
    initialization="random", learning_rate=200, n_iter=750
).fit(x)

@@

Embedding single cells into existing reference atlases can also be useful for
cell-type classification in cases of unknown cell identities. For instance, in
Fig.~\ref{fig:transform}, we construct a reference embedding (using the same code snippet as above) using labeled data
from \citet{hochgerner2018conserved} containing gene-expression profiles of
cells from the mouse brain. The authors assign a type to each cell. We can
verify their classification accuracy by visualizing the expression of
well-established gene markers for the major cell types. We then embed cells
from \citet{harris2018classes} into the constructed cell atlas. In
\citet{harris2018classes}, labels are provided only for neuronal cells. In the
resulting mapping, we can quickly identify other non-neuronal cell types,
including oligodendrocytes and astrocytes. We can further use marker genes to
validate that the mapping in the reference landscape is correct.

@@

\section{Discussion} \label{sec:discussion}

@@

% We benchmark Python
Fig.~\ref{fig:benchmarks_py} benchmarks four popular \proglang{Python}~\citep{vanrossum1995python} t-SNE
implementations, including \pkg{scikit-learn} (v1.0.1), \pkg{MulticoreTSNE}
(v0.1), \pkg{FIt-SNE} (v1.1.0), and \opentsne\ (v0.6.2). Benchmarks were
performed on an Intel(R) Xeon(R) CPU E5-1650 equipped with 128 GB of memory.
Benchmarks were run for $1,000$ iterations with the original t-SNE parameters,
as some implementations do not allow for their modification. To ensure a
realistic benchmarking scenario, we utilize the 10X Genomics 1.3 million mouse
brain data set~\citep{xxx}, containing 1.3 million single-cell gene-expression
profiles. We preprocess the data using the standard single-cell analysis
pipeline~\citep{xxx} and extract the top 50 principal components. To generate
benchmark data sets of different sample sizes, we subsample the data set five
times at each sample size. In total, we run each implementation on 30 different
data sets.

@@

% Problem with Python
In \proglang{Python}, the most widely-used implementation of t-SNE comes from \pkg{scikit-learn}, which exhibits long runtimes when compared to other \proglang{Python} implementations. \pkg{scikit-learn}, like its \proglang{C++} counterpart -- \pkg{MulticoreTSNE}~\citep{Ulyanov2016} , is based on the Barnes-Hut approximation scheme. However, as shown on Fig.~\ref{fig:benchmarks_py}, \pkg{scikit-learn} exhibits much longer runtimes than \pkg{MulticoreTSNE}. Newer implementations, such as \pkg{FIt-SNE} and \opentsne, both implement the FIt-SNE approximation scheme, making them suitable for the visualization of millions of data points. While both libraries implement the same algorithm, \opentsne\ emphasizes ease of use and extensibility and is primarily written in \proglang{Python}, which inevitably introduces some runtime overhead. This makes \opentsne\ marginally slower than its pure \proglang{C++} counterpart -- \pkg{FIt-SNE}. However, these differences disappear almost entirely when utilizing multi-threading, as shown in Fig.~\ref{fig:benchmarks_py}. Additionally, \opentsne\ provides a flexible API, allowing the user to split up the embedding-construction process into several parts. This allows us to cache and reuse intermediate results, enabling users to quickly experiment with different parameter settings and iterate on their final visualizations. This kind of functionality is not supported in other implementations, which require the user to start from scratch for every embedding, resulting in large amounts of redundant computation.

@@

\begin{figure*}[ht]
  \centering
  \includegraphics[width=0.75\textwidth]{benchmarks_langs-final}
  %\includegraphics[width=\textwidth]{benchmarks-combined}
  \caption{\label{fig:benchmarks_lang}
  We select the fastest available, open-source implementations of the t-SNE
  algorithm from the \proglang{Python}, \proglang{R}, and \proglang{Julia}
  programming languages. We choose
  \opentsne\ (v0.6.2) for \proglang{Python}, \pkg{Rtsne}~\citep{krijthe2015rtsne} (v0.15)
  for \proglang{R}, and \pkg{TSne.jl}~\citep{julia_tsne} (v1.3.0) for
  \proglang{Julia}. The benchmarks reflect the time complexity of the
  implemented approximation schemes. For instance, \pkg{TSne.jl} implements a
  naive $\mathcal{O}(N^2)$ algorithm, making it prohibitively expensive for all
  but the smallest of data sets. \pkg{Rtsne} scales similarily to
  \pkg{MulticoreTSNE} in \proglang{Python}, as it implements the $\mathcal{O}(N \log N)$
  Barnes-Hut approximation scheme. Interestingly, the multi-threaded
  implementation version of \pkg{Rtsne} crashes on benchmark data sets
  containing over 500,000 data points due to lack of stack memory. We found
  these crashes to be inconsistent and somewhat random. \opentsne\ is the only
  library implementing the more recent FIt-SNE approximation scheme, which makes
  it suitable for larger data sets.
}
\end{figure*}

@@

We designed \opentsne\ to be accessible to a broader audience. We provide
precompiled binaries for all major \proglang{Python} versions on all major platforms,
making the installation process as seamless as possible. One can install
\opentsne\ through the \proglang{Python} Package Index (\pkg{PyPI}) or \pkg{conda} from the
\pkg{conda-forge} channel, the two most widely adopted Python package managers.
\opentsne's high-level interface is inspired by \pkg{scikit-learn}, which is well
established in the \proglang{Python} data science ecosystem. \opentsne\ implements
multi-threaded versions of both the Barnes-Hut and FIt-SNE approximation
schemes, enabling it to be applied to data sets containing millions of data
points. While the \proglang{Python} virtual machine inevitably introduces some performance
overhead, the runtime is comparable to its \proglang{C++} counterpart -- \pkg{FIt-SNE}.
Finally, \opentsne\ is extensible. Its modular design enables researchers to
quickly experiment with different parameter settings and easily incorporate
custom components into the software. We provide an extended list of features and
comparison to other popular t-SNE implementations in Tab.~\ref{tab:features}.

@@

\toprule
\textbf{Ease of Installation} \\
Native \proglang{Python} installation & \checkmark & & & \checkmark & & \\
\pkg{PyPI} package & \checkmark & \checkmark & & \checkmark & & \\
\pkg{conda} package & \checkmark & & & \checkmark & & \\

@@

We introduce \opentsne, the most feature-complete, open-source, \proglang{Python}
implementation of the widely popular t-SNE visualization algorithm. The library
incorporates the latest developments to the t-SNE algorithm and makes them
easily accessible through a familiar API. \opentsne\ implements efficient
approximation schemes, making it suitable for the visualization of large data
sets containing up to millions of data points. Finally, \opentsne\ is easy to
install and comes with precompiled binaries available for all major platforms.
